Methodology for Assessing the State of the Practice for Domain X

### 2020-10-15 StateOfPractice/Methodology/Methodology.tex
updated section 6 of Methodology

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The initial list of candidate software packages should first be filtered to a manageable size. Our target is about 30 packages. We want the list to include packages that are not marked as incomplete and are at least somewhat organized and understandable. We also want the list to be a good representation of the software domain, with packages having enough in common with respect to functionality that it makes sense to compare the software. The initial list of candidate software should be filtered using the following properties sequentially:

\begin{enumerate}
	\item Scope: The functionality of the domain software should be increasingly specific.
	\item Usage: The installation procedure should appear to be clear or easy to figure out.
    \item Age: Ideally the latest release or source code commit should be relatively recent, such as within the last 5 years, unless the candidate software appears to be well recommended and currently in use.
\end{enumerate}

>>>>

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
If the list of software is too long (over around 30 packages), then steps need to be taken to create a more manageable list. To reduce the length of the list, the following filters are applied in the priority order listed, stopping once the desired number of projects is reached:

\begin{enumerate}
	\item Scope: The functionality of the domain software should be increasingly specific.
	\item Usage: The installation procedure should appear to be clear or easy to figure out.
    \item Age: Ideally the latest release or source code commit should be relatively recent for software in the domain unless the candidate software appears to be well recommended and currently in use.
\end{enumerate}
